What We Eval in the Shadows

### 2021-04-15 paper/main.tex
Explain polymorphism in minimized expressions

%TODO Add a simple example of a slot lookup (very common with match.call)
Slot lookup happens very often to evaluate some of the elements of a call list returned by \c{match.call}.
For instance in the \emph{blme} package:
\begin{lstlisting}
matchedCall <- match.call()
...
df <- eval(matchedCall$df)
\end{lstlisting}

>>>>

Slot lookup happens very often to evaluate some of the elements of a call list returned by \c{match.call}.
For instance in the \emph{pwrFDR} package:
\begin{lstlisting}
m <- match.call()
...
average.power <- m$average.power <- eval(m$average.power, sys.parent())
\end{lstlisting}

Here, \c{m\$average.power}, depending on the shape of the arguments to the surrounding function,  can be resolved to a variable, a more complex expression, or a number, leading to several possible minimized expressions, including \c{X} and \c{V}.
